Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-25 02_methods/methods.tex
Finish the first draft
Added the missing figure

\begin{figure}
  \centering
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pathist}\includegraphics[width=.35\textwidth]{02_methods/figures/IMG_20160824_122328.jpg}} \hfill
  \subfigure[]{\label{subfig:heatmaprep}\includegraphics[width=.5\textwidth]{02_methods/figures/pat2.pdf}}
  \hspace*{\fill}
  \\
  \hspace*{\fill}
  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat1.pdf}} \hfill
  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}} \hfill
  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the variations of the intensity \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
  \label{fig:heatmap}
\end{figure}

In \ac{dce}-\ac{mri}, the intensity \ac{pdf} does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathist}.
Indeed, the inter-patient variations are more complex due to the temporal acquisition.
A better representation to observed these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time (see Fig.\,\ref{subfig:pathist}) using a heatmap representation as shown in Fig.\,\ref{subfig:heatmaprep}.
Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
(i) an intensity offset $\Delta_i$ of the \ac{pdf} peak at pre-contrast,
(ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
(iii) a change of scale $\sigma_i$ related to the signal enhancement.
Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.

@@

\begin{figure}
  \centering
  \hspace*{\fill}
  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse.pdf}} \hfill
  \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the correction of the time offset and the data dispersion.}
  \label{fig:curveal}
\end{figure}

@@

\begin{figure}
  \centering
  \hspace*{\fill}
  \subfigure[Original image.]{\label{fig:org}\includegraphics[width=.3\textwidth]{02_methods/figures/original.pdf}} \hfill
  \subfigure[Candidates region after clustering.]{\label{fig:cand}\includegraphics[width=.3\textwidth]{02_methods/figures/candidate.pdf}} \hfill
  \subfigure[Regions selected after applying the different criteria.]{\label{fig:final}\includegraphics[width=.3\textwidth]{02_methods/figures/aif.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the segmentation of the area used to determine the \acs*{aif}.}
  \label{fig:aif}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pathist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
  \hspace*{\fill}
  \\
  \hspace*{\fill}
  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat1.pdf}} \hfill
  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}} \hfill
  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the variations of the intensity \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
  \label{fig:heatmap}
\end{figure*}

In \ac{dce}-\ac{mri}, the intensity \ac{pdf} does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathist}.
Indeed, the inter-patient variations are more complex due to the temporal acquisition.
A better representation to observed these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
(i) an intensity offset $\Delta_i$ of the \ac{pdf} peak at pre-contrast,
(ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
(iii) a change of scale $\sigma_i$ related to the signal enhancement.
Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.

@@

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse.pdf}} \hfill
  \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the correction of the time offset and the data dispersion.}
  \label{fig:curveal}
\end{figure*}

@@

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[Original image.]{\label{fig:org}\includegraphics[width=.3\textwidth]{02_methods/figures/original.pdf}} \hfill
  \subfigure[Candidates region after clustering.]{\label{fig:cand}\includegraphics[width=.3\textwidth]{02_methods/figures/candidate.pdf}} \hfill
  \subfigure[Regions selected after applying the different criteria.]{\label{fig:final}\includegraphics[width=.3\textwidth]{02_methods/figures/aif.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the segmentation of the area used to determine the \acs*{aif}.}
  \label{fig:aif}
\end{figure*}
